---
title: "Publications"
---

## Journal articles

```{r}
#| echo: false
#| message: false
#| eval: false
# this section is run manually to obtain
# publication list 
# orcid exported bibtex in wrong format
#library(RefManageR)
#b <- ReadBib("citations-gc.bib")
#b
library(rorcid)
library(dplyr)
b <- works("0000-0002-3813-7155")
pubs <- tibble(title = b$title.title.value, 
               year = b$`publication-date.year.value`,
               journal = b$`journal-title.value`,
               doi = b$url.value) |>
  arrange(desc(year))
save(pubs, file="pubs.rda")
```

```{r}
#| echo: false
#| message: false
#library(knitr)
#library(kableExtra)
library(dplyr)
library(glue)
library(gt)
load("pubs.rda")
pubs <- pubs |>
  mutate(titlelink = glue("[{title}]({doi})"))
#kable(pubs)
pubs |> 
  select(titlelink, year, journal) |>
  gt() |>
  gt::fmt_markdown(columns = titlelink) |>
  cols_label(titlelink = "title") |> 
  gt::cols_width(titlelink ~ px(500),
                 year ~ px(50),
                 journal ~ px(200)) |>
  cols_align("left")
  
```

::: {style="font-size: 60%"}
*This list is automatically populated from orcid.org*
:::

## Books 

- Cook, D. and Laa, U. (2024) [Interactively exploring high-dimensional data and models in R](https://dicook.github.io/mulgar_book/), CRC Press.
- Cook, D., and Swayne, D. (with contributions from Buja, A., Temple Lang, D., Hofmann, H., Wickham, H. and Lawrence, M.) (2007). Interactive and Dynamic Graphics for Data Analysis with examples using R and GGobi, Springer, New York. With additional data, R code and demo movies at [http://www.ggobi.org](http://www.ggobi.org).

## Refereed conference proceedings

## Media